A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-14 papers/publication/paper-pollard.tex
Cleaned up some graphics and merged to save space.
Still waiting on some power results that I messed up.

An issue among these systems is the lack of comprehensive comparisons. One possible reason is the considerable effort involved in getting each system to run: satisfying dependencies and ensuring data are correctly formatted are generally nontrivial tasks. Additionally, some systems are developed with large, multi-node clusters in mind while others only work with shared memory, single node computers. An example of the former is GraphX \cite{Xin:2013:GraphX}, which incurs some overhead while gaining fault tolerance and an example of the latter is Ligra \cite{Shun:2013:Ligra}, a framework requiring a shared-memory architecture.
% ``The project was motivated by the fact that the largest publicly available real-world graphs all fit in shared memory''

@@

The complexity of Graphalytics obfuscates the true behavior of the program. By default, Graphalytics generates an HTML report listing the runtimes for each dataset and each algorithm in seconds. For example, one run of a single source shortest paths algorithm took 5.6 seconds. However, perusing the log files reveals a more complete picture: of these 5.96 seconds, 0.21 was spent computing the shortest paths while the remaining time consisted of building the necessary data structures. Furthermore, data such as the number of iterations run for PageRank is not easily available using Graphalytics.
% We use GraphMat, the single source shortest paths algorithm, the dota-league dataset from the Game Trace Archive\cite{Guo:2012:GTA}, and the default settings as an example here.
% The full logs:
%Finished setting ids, time: 0.157009
%Starting sort
%Finished sort, time: 1.39571
%Finished setting edge pointers, time: 0.000133
%Starting build_dcsc
%Finished build_dcsc, time: 0.235948
%Finished setting ids, time: 0.154693
%Starting sort
%Finished sort, time: 1.75676
%Finished setting edge pointers, time: 0.000142
%Starting build_dcsc
%Finished build_dcsc, time: 0.238386
%Completed reading A from memory in 4.089144 seconds.
%Completed reading A from file in 5.114708 seconds
%Completed 19 iterations
%Timing results:
%- load graph: 5.11472 sec
%- initialize engine: 2.88486e-05 sec
%- run algorithm: 0.212451 sec
%- print output: 0.0799532 sec
%- deinitialize engine: 2.88486e-05 sec
%17:29:05.575 [INFO ] Benchmarking algorithm "Single source shortest paths" on graph "dota-league" took 5955 ms.

@@

\begin{table}[!htb]
	\centering
	\begin{tabular}{l|c|c|c}
		System & Load Graph & \begin{tabular}[x]{@{}c@{}}Construct Data \\ Structure\end{tabular} & Run BFS \\ \hline
		Graph500 & 0.3474 & 0.3971 & 0.003380 \\
		GAP      & 2.351  & 0.1935 & 0.001393 \\
		GraphMat & 0.1511 & 1.101  & 0.1031 \\
		GraphBIG & 37.22  & N/A    & 0.1528 \\
	\end{tabular}
	\caption{The above table shows times for $2^{20}$ verties and the times are in seconds. The Graph500 generates the graph instead of loading it into a file. GraphBIG builds the graph and reads in the file simultaneously. These results were averaged across 32 roots.}
	\label{tab:fileload}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=0.6\columnwidth, trim=0 36pt 18pt 0, clip]{graphics/bfs_time.pdf}
	\caption{The $y$-axis is logarithmic.}
	\label{fig:bfs-time}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.6\columnwidth, trim=0 36pt 18pt 0, clip]{graphics/bfs_dsc.pdf}
	\caption{The $y$-axis is logarithmic. GraphBIG reads in the file and generates the data structure simultaneously so is omitted.}
	\label{fig:bfs-dsc}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.6\columnwidth, trim=0 36pt 18pt 0, clip]{graphics/pr_time.pdf}
	\caption{The $y$-axis is logarithmic. GraphMat continues to run until none of the vertices' ranks change. [There is only one data point]}
	\label{fig:pr-time}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.6\columnwidth, trim=0 36pt 18pt 0, clip]{graphics/pr_iters.pdf}
	\caption{The $y$-axis \emph{not} logarithmic. GraphMat iterations are measured differently because of the ``think like a vertex'' paradigm and runs until none of the vertices' ranks change.}
	\label{fig:pr-iters}
\end{figure}
[Note that for figure Fig.\ref{fig:pr-iters}, mention time per iteration]

>>>>

An overarching issue among these systems is the lack of comprehensive comparisons. One possible reason is the considerable effort involved in getting each system to run: satisfying dependencies and ensuring data are correctly formatted are generally nontrivial tasks. Additionally, some systems are developed with large, multi-node clusters in mind while others only work with shared memory, single node computers. An example of the former is GraphX \cite{Xin:2013:GraphX}, which incurs some overhead while gaining fault tolerance and an example of the latter is Ligra \cite{Shun:2013:Ligra}, a framework requiring a shared-memory architecture.
% ``The project was motivated by the fact that the largest publicly available real-world graphs all fit in shared memory''

@@

The complexity of Graphalytics obfuscates the true behavior of the program. By default, Graphalytics generates an HTML report listing the runtimes for each dataset and each algorithm in seconds. For example, one run of a single source shortest paths algorithm took 5.6 seconds. However, perusing the log files reveals a more complete picture: of these 5.96 seconds, 0.21 was spent computing the shortest paths while the remaining time consisted of building the necessary data structures. Furthermore, data such as the number of iterations run for PageRank is not easily available using Graphalytics.
%We use GraphMat, the single source shortest paths algorithm, the dota-league dataset from the Game Trace Archive\cite{Guo:2012:GTA}, and the default settings as an example here.
% The full logs:
%Finished setting ids, time: 0.157009
%Starting sort
%Finished sort, time: 1.39571
%Finished setting edge pointers, time: 0.000133
%Starting build_dcsc
%Finished build_dcsc, time: 0.235948
%Finished setting ids, time: 0.154693
%Starting sort
%Finished sort, time: 1.75676
%Finished setting edge pointers, time: 0.000142
%Starting build_dcsc
%Finished build_dcsc, time: 0.238386
%Completed reading A from memory in 4.089144 seconds.
%Completed reading A from file in 5.114708 seconds
%Completed 19 iterations
%Timing results:
%- load graph: 5.11472 sec
%- initialize engine: 2.88486e-05 sec
%- run algorithm: 0.212451 sec
%- print output: 0.0799532 sec
%- deinitialize engine: 2.88486e-05 sec
%17:29:05.575 [INFO ] Benchmarking algorithm "Single source shortest paths" on graph "dota-league" took 5955 ms.

@@

Table~\ref{tab:epg-perf}, we show the performance results of running graphalytics and our approach using the same, synthetic dataset. Now, our approach computes multiple runs whereas graphalytics only uses one root for BFS. This gives a better picture of algorithm reliability and is explained further.

\begin{table}
	\centering
	\begin{tabular}{l|c|c|c}
		System & Load Graph & \begin{tabular}[x]{@{}c@{}}Construct Data \\ Structure\end{tabular} & Run BFS \\ \hline
		Graph500 & 0.3474 & 0.3971 & 0.003380 \\
		GAP      & 2.351  & 0.1935 & 0.001393 \\
		GraphMat & 0.1511 & 1.101  & 0.1031 \\
		GraphBIG & 37.22  & N/A    & 0.1528 \\
	\end{tabular}
	\caption{The above table shows times for $2^{20}$ verties and the times are in seconds. The Graph500 generates the graph instead of loading it into a file. GraphBIG builds the graph and reads in the file simultaneously. These results were averaged across 32 roots.}
	\label{tab:epg-perf}
\end{table}

\begin{figure}
	\centering
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/bfs_time.pdf}
	\end{minipage}
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/bfs_dsc.pdf}
	\end{minipage}
	\caption{The $y$-axis is logarithmic. GraphBIG reads in the file and generates the data structure simultaneously so is omitted.}
	\label{fig:bfs-time}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/pr_time.pdf}
	\end{minipage}
	\begin{minipage}{0.48\linewidth}
		\includegraphics[width=\linewidth, trim=0 36pt 18pt 0, clip]{graphics/pr_iters.pdf}
	\end{minipage}
	\caption{The $y$-axis is logarithmic. GraphMat continues to run until none of the vertices' ranks change. [There is only one data point] The $y$-axis \emph{not} logarithmic. GraphMat iterations are measured differently because of the ``think like a vertex'' paradigm and runs until none of the vertices' ranks change. [Note that for figure Fig.\ref{fig:pr-iters}, mention time per iteration]}
	\label{fig:pr}
\end{figure}
